The Holy Hand Grenade of Antioch

### 2020-02-22 draft-camelot-holy-grenade.tex
feat: get tex source as close as possible to adoc original

% [NOTE,remove-in-rfc=false]
\begin{note}
  % TODO: \caption{Spamalot}
  The relevance of the musical "Spamalot" to Internet lore should be
  obvious to the reader; but in case of doubt, see also
  Section 1 ("\textbf{What is Spam?}") of RFC2635.
\end{note}

@@

\begin{quote}
  \mn{A. Farrel}
  Although the RFC Editor has recently dragged the IETF kicking and
  screaming into the twentieth century [RFC7990] [RFC7996], there is a
  yearning among all right-thinking Internet architects to "keep it
  simple" and to return to the olden days when pigs could be given
  thrust without anyone taking undue offence.
\end{quote}

@@

\begin{enumerate}
  \item[Trojan Rabbit]
    In their siege of the French-occupied castle which may already
    contain an instance of the Grail, Sir Bedevere the Wise proposes to
    use a Trojan Rabbit to infiltrate the castle, with a raiding party
    to take the French "not only by surprise, but totally unarmed."

@@

\end{enumerate}

@@

The participants of that renowned exercise in cross-cultural
communication, to wit the exchange between the
\textit{Knights of the Round Table}
and the taunting French soldiers serving under 
\textbf{Guy de Lombard} are,
properly speaking, outside the scope of this `menagerie`, being more
% TODO: or less human. Notwithstanding, several^ish^ beasts both animate~d~
and wooden played a significant part in this encounter; most
notably:

* The Projectile Cow, see \mncite{projectile-cow}
* The Trojan Rabbit, see \mncite{trojan-rabbit}

@@

\begin{figure}[h]\centering
  \label{projectile-cow}
  \caption{The Projectile Cow with an accompanying cannon}
  \alt{The Projectile Cow with an accompanying cannon in ASCII}
  \begin{verbatim}
.-.-.-.-.-.-.-.-.-.-.-.--.-.-.-.-.-.-.--.-.-.-.-.-.-.-.--.-.
_-_---__--__--___-___-__-____---___-________---____-____-__-
._.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.--..-.-.-.-.-.-..--.-
,..,.,.,.,.,..,.,,..,.,.,.,.,.,,  ^^  .,,.,.,  ^^   .,.,.,.=
_>-.-.-.-._>_>_>_.-.-.-.-.-.-.-.  \\\  .,.,.  /% // .-.-.-.-.
.,.,.,.,..,.,..,.,.,..,.,.,,..,.,  \ \_______/ /    .,.,.,.,
.,.,.,.,..,.,.,.,..,,..,,.,.,.,.,.  <[ {o} . ]>  #   .,.,.,.
.-.-.--.-.-.-.-.-.--.-.-.-.--.-.-.   [ ______]       .-.-.-.
.-.--.-.-.-.--.-.-.-.--.-.-.,.,.,  / [ !  ` `]   .,.,..,.,.-
.,.,.,.-.-,l,-,l.-,.,.,.,-.,*.    /  {_!MOO!_}    . ., . . ,
.-.-.-.-.-.-.-.-.-.-.-.-.-.-    /M      /    -.-<>.,.,..-.-,
.-.-.--.-.-.-.-.-.-.-.-.--..   /MI    LK\____    .-.-.-.-.-.
.-.-.-.--.-.-.-.-.-.-.-.-.-   /MILK   mil_____k   ,.,.,..-,-
.-,-.-,-.,-.-,-.`-.-/-..     % //   -`  % //      .-.p . .-.-.
.-.--.-.-.-.-.-.-.-.        % //  .,   % //   .-.-.-.-.-.-.-.-
.-.-.--.-.-.-.-.-.-.  %____============    .-.-.--.-.-.-.-.-
-.-.-.-.--.-.-.-.-.-.      !  !           .,-.-.-,-,--,-.-,-
,--.-.-,--.--.-.,--,        \ \      .-,-,--.-,--,-.---,-.-,
,-.-.-,-,-.-,-,-.--,         +  >    .-,--,-.--,-,-.-.-,--,-
,--.-,--,-,--.---,-               .-,-,--.--,--,-.---,-,-.-.
.,.,.,.,..,.,.,.{A\      .,.,.,.,..,.,.,.,.,.,..,.,.,.,..,.,
.,.,.,.,.,.,.{GLASS\   .,..,.,.,.,.,..,.,.,.,.,.,.,..,.,.,.,
,..,.,,.,,.,{OF|MILK\..,.,.,.,.,..,.,.,.,.,.,..,.,.,.,.,.,.,
,.,..,.,,.,{ISWORTH},.,.,..,.,.,.,.,..,..,.,.,..,.,.,.,.,.,.
.,.,.,.,.{EVERYTNG}.-.-.--..-.-.-.-.--..--.-.-.-.-.--.-.-.-.
-.-.-.-{FORINFANTS}___--___-_-__-___--*(0~`~.,.,.,.,><><.><>
_-__-_{BUTBETTER}-.-,-,-,-,-,-,-,-,.-^^^^.-.-.-.-.^^^7>>>,..
.._...{WITH_HONEY}-.-.-.-.-.-.-.-.-.-.RANDOM(BUSH)SHRUBS>_..
GRASS_GRASS_GRASS_GRASS_GRASS_SOMEROCKS>GRASS>GRASS<GRASS>PC
SOIL_ROOTS_SOIL_SOIL_ROCKS_SOIL_GRASS_GRASS_GRASS_ROCKS_SOIL
CLAY_ROCKS_PEBBLES_CLAY_CLAY_CLAY_CLAY_GOLD_CLAY_CLAY><_WORM
ROOTS_CLAY_SKELETON_MORESOIL_CLAY_CLAY_CLAY_CLAY_<MUSHROOMS>
  \end{verbatim}
\end{figure}

\begin{figure}
  \label{trojan-rabbit}
  \caption{The Trojan Rabbit with an automatic sliding door}
  \alt{The Trojan Rabbit with an automatic sliding door, in ASCII}
  \begin{verbatim}
                           ___  ____
                          //_ \//\__\
                            || ||  |
                         -__||_||__|
                       % //        \--_
                      % //    ____     --___
                     % //    % //  \         \-_
                    % //     \\  @/        o ||
                   % //       ----      _____||
                  % //                  //
             //\_//__                 //
           //--  --- \____           //
          % //         --- \______   //
         % //  , .          ----- \_//_
        % //      ,.               --- \____
       % //             .,v             --- \___
      % //                                __ -- \_
     ||  ,         _______________       //||     |-_
     ||           |   |''''''''''|     % //||     |  |
     ||     '     |   |          |        ||     |  |
     ||           |   |          |        ||     |  |
     ||      "    |   | 0        |     ___||___  |  |
     ||           |   |          |     --------  |  |
     ||___        |   |          |        ______ |  |-
    % //    \      |   |          |       % //    \| _| \
   % //      \ ____|---|__________|______% //      \/    |
  ||    X    |      /                  ||    X    |   /
   \\       /\\____/                    \\       /___/
    \\_____/ -----                       \\_____/---
     -----                                -----
  \end{verbatim}
\end{figure}

@@

\begin{itemize}
  \item Less overall screen-time dedicated to the Trojan Rabbit.

  \item The Trojan Rabbit as projectile has already been anticipated
  by the Cow as projectile.
\end{itemize}
\end{aside}

@@

\begin{note}{display=true,source=Author}
Image courtesy of
https://camelot.gov.example/creatures-in-ascii/
\end{note}

@@

The exchange of projectile animals was the beginning of a
long-running fruitful relationship between the British and the
French peoples,
\begin{comment}TODO: Will need to verify that claim.\end{comment} which
arguably predates the traditional English enmity with the
French. \cmt{Strictly speaking, the Knights are Welsh.}

\begin{comment}
This document, as it turns out, has a profusion of XML comments.

@@

\label{caerbannog}
\subsection{The Mythos of Caerbannog}

@@

\label{killer_rabbit_caerbannog}
\subsubsection{The Killer Rabbit of Caerbannog}

@@

\mncite{killer-bunny,The following depiction} of the fearsome beast
has been sourced from
http://camelot.gov.example/avatars/rabbit[Rabbit-SCII],
\mncite{killer-source,accompanied}
by C code that was used in this accurate depiction of the
Killer Rabbit:

@@

\begin{figure}[h]\centering
\label{killer-source}
\begin{sourcecode}{c}
\caption{C Code To Lure Killer Rabbit Back To Cave}
<CODE BEGINS>
/* Locate the Killer Rabbit */
int type;
unsigned char *killerRabbit =
  LocateCreature(&caerbannog, "killer rabbit");
if( killerRabbit == 0 ){
  puts("The Killer Rabbit of Caerbannog is out of town.");
  return LOST_CREATURE;
}

@@

/* Finally, notify the Killer Rabbit to act */
return notifyCreature(killerRabbit, &carrot);
<CODE ENDS>
\end{sourcecode}
\end{figure}

@@

\label{holy_hand_grenade}
\subsubsection{Holy Hand Grenade of Antioch}

@@

\begin{figure}[h]\centering
\label{hand-grenade-figure}
\caption{The Holy Hand Grenade of Antioch (don't pull the pin)}
% [alt=Holy Hand Grenade of Antioch, in ASCII]
\begin{verbatim}
                        ______
                       \\/  \/
                      __\\  /__
                     ||  //\   |
                     ||__\\/ __|
                        ||  |    ,---,
                        ||  |====`\  |
                        ||  |    '---'
                      ,--'*`--,
                    _||#|***|#|
                 _,/.-'#|   |#`-._
               ,,-'#####|   |#####`-.
             ,,'########|   |########`,
            //##########| o |##########\
           ||###########|   |###########|
          ||############| o |############|
          ||------------'   '------------|
          ||o  o  o  o  o   o  o  o  o  o|
           |-----------------------------|
           ||###########################|
            \\#########################/
             `..#####################,'
               ``..###############_,'
                  ``--.._____..--'
                     `''-----''`
\end{verbatim}
\end{figure}

@@

\begin{figure}[h]\centering
\label{sovereign-orb}
\caption{The Sovereign's Orb made invisible}

  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{example-image-a}
    \caption{Outlines of the Sovereign's Orb}
% TODO PB
%[link=https://camelot.gov.example/sovereigns_orb.jpg,align=right]
%image::https://camelot.gov.example/sovereigns_orb.jpg[Orb,124,135]
    % \includegraphics[width=135,height=124]{https://camelot.gov.example/sovereigns_orb.jpg}
  \end{subfigure}
\end{figure}

@@

The solution to the impasse at the ((Cave of Caerbannog)) was
provided by the successful deployment of the
\textbf{Holy Hand Grenade of Antioch} (see \mncite{hand-grenade-figure})
(((Holy Hand Grenade of Antioch))).
Any similarity between the Holy Hand Grenade of Antioch and the
mythical \textit{Holy Spear of Antioch} is purely intentional;
(((relics, Christian))) any similarity between the Holy Hand Grenade
of Antioch and the \textit{Sovereign's Orb of the United Kingdom}
(see \mncite{sovereign-orb}) is putatively fortuitous.
(((relics, monarchic)))

@@

Holy Hand Grenade of Antioch::
  Ordnance deployed by Brother Maynard under the incantation of a
  lector, in order to dispense with the Foes of the Virtuous.
  See \mncite{hand-grenade-figure}.

Holy Spear of Antioch::
  A supposed relic of the crucifixion of Jesus Christ, this is one
  of at least four claimed instances of the lance that pierced
  Christ's side. Its historical significance lies in inspiring
  crusaders to continue their siege of Antioch in 1098.

Sovereign's Orb of the United Kingdom::
  Part of the Crown Jewels of the United Kingdom, the Sovereign's
  Orb is a hollow gold sphere set with jewels and topped with a
  cross.  It was made for Charles II in 1661. 
  See \mncite{sovereign-orb}.

@@

\begin{enumerate}
  \item Preamble: St Attila Benediction
  \item Feast of the People on Sundry Foods
    \begin{itemize}
      \item Lambs
      \item Sloths
      \item Carp
      \item Anchovies
      \item Orangutangs
      \item Breakfast Cereals
      \item Fruit Bats
      \item \textit{et hoc genus omne}
    \end{itemize}

  \item Take out the Holy Pin
  \item The Count

  \begin{enumerate}
  %[upperalpha]
    \item Count is to Three: no more, no less
    \item Not Four
    \item Nor Two, except if the count then proceeds to Three
    \item Five is Right Out
  \end{enumerate}

  \item Lob the Holy Hand Grenade of Antioch towards the Foe
  \item The Foe, being naughty in the \textbf{LORD's} sight, \bcp{shall} snuff it

\end{enumerate}

@@

\begin{enumerate}
  \item Take out the Holy Pin
  \item The Count

\begin{verbatim}
integer count;
for count := 1 step 1 until 3 do
  say(count)
comment Five is Right Out
\end{verbatim}

  \item Lob the Holy Hand Grenade of Antioch towards the Foe
  \item Foe snuffs it

\end{enumerate}

@@

% TODO: [grid=all,options="footer"]
% \begin{longtabu} to \linewidth {|l|l|}
\begin{longtable}{|l|l|}

@@

\begin{quote}
% .כאן אולי ימצאו המילים האחרונות של יוסף מארמתיה
% .מי אשר יהיה אמיץ ובעל נפש טהורה יוכל למצוא את הגביע הקדוש בטירת אאאאאאאה

@@

\subsection{Normative References}
\begin{thebibliography}{1}
  \bibitem{RFC2119} 
\end{thebibliography}

\subsection{Informative References}
\begin{thebibliography}{1}

% TODO
% \begin{verbatim}
% <reference anchor="grail_film">
%   <front>
%     <title>Monty Python and the Holy Grail</title>
%     <author initials="G." surname="Chapman"/>
%     <author initials="J." surname="Cleese"/>
%     <author initials="E." surname="Idle"/>
%     <author initials="T." surname="Gilliam"/>
%     <author initials="T." surname="Jones"/>
%     <author initials="M." surname="Palin"/>
%     <date year="1975"/>
%   </front>
% </reference>
% \end{verbatim}

  \bibitem{RFC2635} 
  \bibitem{RFC7990}
  \bibitem{RFC8140}
  \bibitem{RFC8174}

\end{thebibliography}

>>>>

\begin{note}
  \mn{remove-in-rfc=false}
  \caption{Spamalot}
  The relevance of the musical "Spamalot" to Internet lore should be
  obvious to the reader; but in case of doubt, see also
  Section 1 ("\textbf{What is Spam?}") of RFC2635.
\end{note}

@@

\begin{quote}
  \mn{attribution="A. Farrel"}
  Although the RFC Editor has recently dragged the IETF kicking and
  screaming into the twentieth century [RFC7990] [RFC7996], there is a
  yearning among all right-thinking Internet architects to "keep it
  simple" and to return to the olden days when pigs could be given
  thrust without anyone taking undue offence.
\end{quote}

@@

\begin{description}
  \item[Trojan Rabbit]
    In their siege of the French-occupied castle which may already
    contain an instance of the Grail, Sir Bedevere the Wise proposes to
    use a Trojan Rabbit to infiltrate the castle, with a raiding party
    to take the French "not only by surprise, but totally unarmed."

@@

\end{description}

@@

The participants of that renowned exercise in cross-cultural
communication, to wit the exchange between the
\textit{Knights of the Round Table}
and the taunting French soldiers serving under 
\textbf{Guy de Lombard} are,
% TODO: properly speaking, outside the scope of this `menagerie`, being more
% TODO: or less human. Notwithstanding, several^ish^ beasts both animate~d~
and wooden played a significant part in this encounter; most
notably:

\begin{itemize}
  \item The Projectile Cow, see \mncite{projectile-cow}
  \item The Trojan Rabbit, see \mncite{trojan-rabbit}
\end{itemize}

@@

\begin{figure}[h]\centering
  \mn{alt=The Projectile Cow with an accompanying cannon in ASCII}
  \label{projectile-cow}
  \caption{The Projectile Cow with an accompanying cannon}
  \begin{verbatim}
.-.-.-.-.-.-.-.-.-.-.-.--.-.-.-.-.-.-.--.-.-.-.-.-.-.-.--.-.
_-_---__--__--___-___-__-____---___-________---____-____-__-
._.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.--..-.-.-.-.-.-..--.-
,..,.,.,.,.,..,.,,..,.,.,.,.,.,,  ^^  .,,.,.,  ^^   .,.,.,.=
_>-.-.-.-._>_>_>_.-.-.-.-.-.-.-.  \\\  .,.,.  /% // .-.-.-.-.
.,.,.,.,..,.,..,.,.,..,.,.,,..,.,  \ \_______/ /    .,.,.,.,
.,.,.,.,..,.,.,.,..,,..,,.,.,.,.,.  <[ {o} . ]>  #   .,.,.,.
.-.-.--.-.-.-.-.-.--.-.-.-.--.-.-.   [ ______]       .-.-.-.
.-.--.-.-.-.--.-.-.-.--.-.-.,.,.,  / [ !  ` `]   .,.,..,.,.-
.,.,.,.-.-,l,-,l.-,.,.,.,-.,*.    /  {_!MOO!_}    . ., . . ,
.-.-.-.-.-.-.-.-.-.-.-.-.-.-    /M      /    -.-<>.,.,..-.-,
.-.-.--.-.-.-.-.-.-.-.-.--..   /MI    LK\____    .-.-.-.-.-.
.-.-.-.--.-.-.-.-.-.-.-.-.-   /MILK   mil_____k   ,.,.,..-,-
.-,-.-,-.,-.-,-.`-.-/-..     % //   -`  % //      .-.p . .-.-.
.-.--.-.-.-.-.-.-.-.        % //  .,   % //   .-.-.-.-.-.-.-.-
.-.-.--.-.-.-.-.-.-.  %____============    .-.-.--.-.-.-.-.-
-.-.-.-.--.-.-.-.-.-.      !  !           .,-.-.-,-,--,-.-,-
,--.-.-,--.--.-.,--,        \ \      .-,-,--.-,--,-.---,-.-,
,-.-.-,-,-.-,-,-.--,         +  >    .-,--,-.--,-,-.-.-,--,-
,--.-,--,-,--.---,-               .-,-,--.--,--,-.---,-,-.-.
.,.,.,.,..,.,.,.{A\      .,.,.,.,..,.,.,.,.,.,..,.,.,.,..,.,
.,.,.,.,.,.,.{GLASS\   .,..,.,.,.,.,..,.,.,.,.,.,.,..,.,.,.,
,..,.,,.,,.,{OF|MILK\..,.,.,.,.,..,.,.,.,.,.,..,.,.,.,.,.,.,
,.,..,.,,.,{ISWORTH},.,.,..,.,.,.,.,..,..,.,.,..,.,.,.,.,.,.
.,.,.,.,.{EVERYTNG}.-.-.--..-.-.-.-.--..--.-.-.-.-.--.-.-.-.
-.-.-.-{FORINFANTS}___--___-_-__-___--*(0~`~.,.,.,.,><><.><>
_-__-_{BUTBETTER}-.-,-,-,-,-,-,-,-,.-^^^^.-.-.-.-.^^^7>>>,..
.._...{WITH_HONEY}-.-.-.-.-.-.-.-.-.-.RANDOM(BUSH)SHRUBS>_..
GRASS_GRASS_GRASS_GRASS_GRASS_SOMEROCKS>GRASS>GRASS<GRASS>PC
SOIL_ROOTS_SOIL_SOIL_ROCKS_SOIL_GRASS_GRASS_GRASS_ROCKS_SOIL
CLAY_ROCKS_PEBBLES_CLAY_CLAY_CLAY_CLAY_GOLD_CLAY_CLAY><_WORM
ROOTS_CLAY_SKELETON_MORESOIL_CLAY_CLAY_CLAY_CLAY_<MUSHROOMS>
  \end{verbatim}
\end{figure}

\begin{figure}
  \mn{alt=The Trojan Rabbit with an automatic sliding door, in ASCII}
  \label{trojan-rabbit}
  \caption{The Trojan Rabbit with an automatic sliding door}
  \begin{verbatim}
                           ___  ____
                          //_ \//\__\
                            || ||  |
                         -__||_||__|
                       % //        \--_
                      % //    ____     --___
                     % //    % //  \         \-_
                    % //     \\  @/        o ||
                   % //       ----      _____||
                  % //                  //
             //\_//__                 //
           //--  --- \____           //
          % //         --- \______   //
         % //  , .          ----- \_//_
        % //      ,.               --- \____
       % //             .,v             --- \___
      % //                                __ -- \_
     ||  ,         _______________       //||     |-_
     ||           |   |''''''''''|     % //||     |  |
     ||     '     |   |          |        ||     |  |
     ||           |   |          |        ||     |  |
     ||      "    |   | 0        |     ___||___  |  |
     ||           |   |          |     --------  |  |
     ||___        |   |          |        ______ |  |-
    % //    \      |   |          |       % //    \| _| \
   % //      \ ____|---|__________|______% //      \/    |
  ||    X    |      /                  ||    X    |   /
   \\       /\\____/                    \\       /___/
    \\_____/ -----                       \\_____/---
     -----                                -----
  \end{verbatim}
\end{figure}

@@

  \begin{itemize}
    \item Less overall screen-time dedicated to the Trojan Rabbit.
    \item The Trojan Rabbit as projectile has already been anticipated
    by the Cow as projectile.
  \end{itemize}
\end{aside}

@@

\begin{note}
  \mn{display=true,source=Author}
  Image courtesy of
  % TODO \href apparently not working
  {https://camelot.gov.example/creatures-in-ascii/}
\end{note}

@@

The exchange of projectile animals was the beginning of a
long-running fruitful relationship between the British and the
French peoples, which
arguably predates the traditional English enmity with the
French.

% TODO: is this a comment?
\begin{comment}
  TODO: Will need to verify that claim.
\end{comment}

% TODO: is this a comment?
\begin{comment}
  Strictly speaking, the Knights are Welsh.
\end{comment}

% TODO: this is a comment, but how should it be formatted?
\begin{comment}
This document, as it turns out, has a profusion of XML comments.

@@

\subsection{The Mythos of Caerbannog}
\label{caerbannog}

@@

\subsubsection{The Killer Rabbit of Caerbannog}
\label{killer_rabbit_caerbannog}
% TODO: this label ain't behaving -- why?

@@

\mncite{killer-bunny,The following depiction} of the fearsome beast
has been sourced from
\url{http://camelot.gov.example/avatars/rabbit[Rabbit-SCII]},
\mncite{killer-source,accompanied}
by C code that was used in this accurate depiction of the
Killer Rabbit:

@@

% TODO: is this figure environment avoidable?
\begin{figure}[h]\centering
\label{killer-source}
\caption{C Code To Lure Killer Rabbit Back To Cave}
% TODO: \mn{source,c,markers=true}
\begin{sourcecode}
/* Locate the Killer Rabbit */
int type;
unsigned char *killerRabbit =
  LocateCreature(&caerbannog, "killer rabbit");
if( killerRabbit == 0 ){
  puts("The Killer Rabbit of Caerbannog is out of town.");
  return LOST_CREATURE;
}

@@

/* Finally, notify the Killer Rabbit to act */
return notifyCreature(killerRabbit, &carrot);
\end{sourcecode}
\end{figure}

@@

\subsubsection{Holy Hand Grenade of Antioch}
\label{holy_hand_grenade}

@@

% TODO: wrapping figure should not be rendered to ADOC for verbatim
\begin{figure}[h]\centering
\label{hand-grenade-figure}
\caption{The Holy Hand Grenade of Antioch (don't pull the pin)}
% [alt=Holy Hand Grenade of Antioch, in ASCII]
\begin{verbatim}
                        ______
                       \\/  \/
                      __\\  /__
                     ||  //\   |
                     ||__\\/ __|
                        ||  |    ,---,
                        ||  |====`\  |
                        ||  |    '---'
                      ,--'*`--,
                    _||#|***|#|
                 _,/.-'#|   |#`-._
               ,,-'#####|   |#####`-.
             ,,'########|   |########`,
            //##########| o |##########\
           ||###########|   |###########|
          ||############| o |############|
          ||------------'   '------------|
          ||o  o  o  o  o   o  o  o  o  o|
           |-----------------------------|
           ||###########################|
            \\#########################/
             `..#####################,'
               ``..###############_,'
                  ``--.._____..--'
                     `''-----''`
\end{verbatim}
\end{figure}

@@

\begin{figure}[h]\centering
  \mn{foo}
  \label{sovereign-orb}
  \caption{The Sovereign's Orb made invisible}
  % TODO: \mn{link=https://upload.wikimedia.org/wikipedia/commons/b/bf/Coa_Illustration_Elements_Globus_cruciger.svg,align=right}
  % TODO: image::https://camelot.gov.example/sovereigns_orb.jpg[Orb,124,135]
  %       \includegraphics[width=135,height=124]{https://camelot.gov.example/sovereigns_orb.jpg}
  \includegraphics[width=\textwidth]{example-image-a}
\end{figure}

@@

% TODO: what are (((...))) ?
The solution to the impasse at the ((Cave of Caerbannog)) was
provided by the successful deployment of the
\textbf{Holy Hand Grenade of Antioch} (see \mncite{hand-grenade-figure})
(((Holy Hand Grenade of Antioch))).
Any similarity between the Holy Hand Grenade of Antioch and the
mythical \textit{Holy Spear of Antioch} is purely intentional;
(((relics, Christian))) any similarity between the Holy Hand Grenade
of Antioch and the \textit{Sovereign's Orb of the United Kingdom}
(see \mncite{sovereign-orb}) is putatively fortuitous.
(((relics, monarchic)))

@@

\begin{description}
  \item[Holy Hand Grenade of Antioch]
    Ordnance deployed by Brother Maynard under the incantation of a
    lector, in order to dispense with the Foes of the Virtuous.
    See \mncite{hand-grenade-figure}.
  \item[Holy Spear of Antioch]
    A supposed relic of the crucifixion of Jesus Christ, this is one
    of at least four claimed instances of the lance that pierced
    Christ's side. Its historical significance lies in inspiring
    crusaders to continue their siege of Antioch in 1098.
  \item[Sovereign's Orb of the United Kingdom]
    Part of the Crown Jewels of the United Kingdom, the Sovereign's
    Orb is a hollow gold sphere set with jewels and topped with a
    cross.  It was made for Charles II in 1661. 
    See \mncite{sovereign-orb}.
\end{description}

@@

\begin{enumerate}
  \item Preamble: St Attila Benediction
  \item Feast of the People on Sundry Foods
    \begin{itemize}
      \item Lambs
      \item Sloths
      \item Carp
      \item Anchovies
      \item Orangutangs
      \item Breakfast Cereals
      \item Fruit Bats
      \item \textit{et hoc genus omne}
    \end{itemize}
  \item Take out the Holy Pin
  \item The Count
    \begin{enumerate}% TODO: [upperalpha]
      \item Count is to Three: no more, no less
      \item Not Four
      \item Nor Two, except if the count then proceeds to Three
      \item Five is Right Out
    \end{enumerate}
  \item Lob the Holy Hand Grenade of Antioch towards the Foe
  \item The Foe, being naughty in the \textbf{LORD's} sight, \bcp{shall} snuff it
\end{enumerate}

@@

\begin{enumerate}
  \item Take out the Holy Pin
  \item The Count
    \begin{verbatim}
    integer count;
    for count := 1 step 1 until 3 do
      say(count)
    comment Five is Right Out
    \end{verbatim}
  \item Lob the Holy Hand Grenade of Antioch towards the Foe
  \item Foe snuffs it
\end{enumerate}

@@

% TODO: table rendering is not advanced enough right now!
% TODO: [grid=all,options="footer"]
% \begin{longtabu} to \linewidth {|l|l|}
\begin{longtable}{|l|l|}

@@

\begin{quote}
  \mn{Joseph of Arimathea, https://context.reverso.net}
% .כאן אולי ימצאו המילים האחרונות של יוסף מארמתיה
% .מי אשר יהיה אמיץ ובעל נפש טהורה יוכל למצוא את הגביע הקדוש בטירת אאאאאאאה

@@

% TODO: bibliography with custom title \subsection{Normative References}
\begin{thebibliography}{1}
  \bibitem[RFC 2119]{RFC2119}
\end{thebibliography}

% TODO: bibliography with custom title \subsection{Informative References}
\begin{thebibliography}{1}
  \bibitem[Grail]{grail_film}
    G. Chapman, J. Cleese, E. Idle, T. Gilliam, T. Jones, M. Palin. 1975. \textit{Monty Python and the Holy Grail}.
  \bibitem[RFC 2635]{RFC2635}
  \bibitem[RFC 7990]{RFC7990}
  \bibitem[RFC 8140]{RFC8140}
  \bibitem[RFC 8174]{RFC8174}
\end{thebibliography}
